---
title: "Schurniverse"
author: "Melvin Adkins"
date: "2023-03-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Melvin Adkins - Preprocessing 1

```{r}
#setwd("C:/Users/15639/Documents/Courses/Distributed_Computing")
```


## 2. Load in data with appropriate NA values
```{r}
gp <- read.csv("C:/Users/15639/Documents/Courses/Data_Visualizations/goodplace.csv", na.strings = c("N/A",""," "))
```

## Cleaning

### 1. Gsub to remove brackets, single quotes, and backslashes

Rating and Warnings
```{r}
gp$Rating <- gsub("\\['|'\\]", "", gp$Rating)
gp$Warnings <- gsub("\\['|'\\]", "", gp$Warnings)
```

Characters
```{r}
gp$Characters <- gsub("'", "", gp$Characters)
gp$Characters <- gsub("\\[|\\]", "", gp$Characters)
gp$Characters <- gsub(", ", "\", \"", gp$Characters)
gp$Characters <- gsub("\"", "", gp$Characters, fixed=TRUE)
gp$Characters <- gsub(",", "", gp$Characters)
gp$Characters[1:10]
```

Fandom
```{r}
gp$Fandom <- gsub("Fandoms:", "", gp$Fandom)
gp$Fandom <- gsub("\n", "", gp$Fandom)
gp$Fandom <- gsub("'", "", gp$Fandom)
gp$Fandom <- gsub("\\[|\\]", "", gp$Fandom)
gp$Fandom <- gsub(", ", "\", \"", gp$Fandom)
gp$Fandom <- gsub("\"", "", gp$Fandom, fixed=TRUE)
gp$Fandom <- gsub(",", "", gp$Fandom)
gp$Fandom[1:10]
```

Words
```{r}
gp$Words <- gsub("<", "", gp$Words)
gp$Words <- gsub("dd", "", gp$Words)
gp$Words <- gsub(" class=", "", gp$Words)
gp$Words <- gsub("\"", "", gp$Words)
gp$Words <- gsub("words>", "", gp$Words)
gp$Words <- gsub("/>", "", gp$Words)
gp$Words <- gsub(",", "", gp$Words)
gp$Words <- as.integer(gp$Words)
gp$Words[1:10]
```

Relationships
```{r}
gp$Relationships <- gsub("'", "", gp$Relationships)
gp$Relationships <- gsub("\\[|\\]", "", gp$Relationships)
gp$Relationships <- gsub(", ", "\", \"", gp$Relationships)
gp$Relationships <- gsub("\"", "", gp$Relationships, fixed=TRUE)
gp$Relationships <- gsub(",", "", gp$Relationships)
gp$Relationships[1:10]
```

Other Tags
```{r}
gp$Other.Tags <- gsub("'", "", gp$Other.Tags)
gp$Other.Tags <- gsub("\\[|\\]", "", gp$Other.Tags)
gp$Other.Tags <- gsub(", ", "\", \"", gp$Other.Tags)
gp$Other.Tags <- gsub("\"", "", gp$Other.Tags, fixed=TRUE)
gp$Other.Tags <- gsub(",", "", gp$Other.Tags)
gp$Other.Tags[1:10]
```

```{r}
head(gp, 10)
```


## 3. Factoring? - Factor some columns to make visualizations easier?
```{r}
# Rating (Gen Audiences, Teen And Up Audiences, Mature, Explicit, Not Rated)
```

Next Steps:

* Further Preprocessing Correct date/possibly split column into multiple columns - Characters: (First Character, Second Character,...etc))/Factoring

* Determine which columns/information will be used in analysis (possibly all collected information)

* Determine what datasets are needed (For analysis and visualization purposes)

* Use of Packages (dplyr/tidyr/tidyverse etc) to make specific/smaller datasets for visualization and analysis purposes
